Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_

### 2021-09-09 supplement/05_calibration_data.Rmd
minor corrections per R1

```{r}
# divide by 1000, convert to integer, then convert to POSIXct
data[, time := as.integer(
  as.numeric(TIME) / 1000
)]
```

@@

# add real duration
patch_summary_real[, duration_real := wp_data]
```

>>>>

```{r}
# divide by 1000, convert to integer
data[, time := as.integer(
  as.numeric(TIME) / 1000
)]
```

@@

# add real duration
patch_summary_real[, duration_real := wp_data]

# write to file
fwrite(patch_summary_real, "data/data_real_watlas_stops.csv")
```

### 2021-09-09 supplement/06_bat_data.Rmd
minor corrections per R1

![A visual examination of plots of the bats' residence patches and linear approximations of paths between them showed that though all three bats roosted at the same site, they used distinct areas of the study site over the three nights **(a)**.
Bats tended to be resident near fruit trees, which are their main food source, travelling repeatedly between previously visited areas **(b, c)**.
However, bats also appeared to spend some time at locations where no fruit trees were recorded, prompting questions about their use of other food sources **(b, c)**.
When bats did occur close together, their residence patches barely overlapped, and their paths to and from the broad area of co-occurrence were not similar **(c)**.
Constructing residence patches for multiple individuals over multiple activity periods suggests interesting dynamics of within- and between-individual overlap **(b, c)**.](../figures/fig_07.png)

>>>>

![A visual examination of plots of the bats' residence patches and linear approximations of paths between them showed that though all three bats roosted at the same site, they used distinct areas of the study site over the three nights **(a)**.
Bats tended to be resident near fruit trees, which are their main food source, travelling repeatedly between previously visited areas **(b, c)**.
However, bats also appeared to spend some time at locations where no fruit trees were recorded, prompting questions about their use of other food sources **(b, c)**.
When bats did occur close together, their residence patches barely overlapped, and their paths to and from the broad area of co-occurrence were not similar **(c)**.
Constructing residence patches for multiple individuals over multiple activity periods suggests interesting dynamics of within- and between-individual overlap **(b, c)**.](../figures/fig_08.png)
